Machine Learning Methods for Site-specific Input Management

### 2022-02-08 Codes/PrepareResults.rmd

# Treatment effect comparison (CF-base vs RF vs BRF)

@@

figure_te <-
  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[, Method := case_when(
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CF_base" ~ "CF-base"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CF-base"))] %>%
  ggplot() +
  geom_point(aes(x = true_tau_base, y = tau_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure
```

>>>>

# Treatment effect comparison

@@

figure_te <-
  here("Shared/Results/for_writing/dt_TEcomparison.rds") %>%
  readRDS() %>%
  .[, Method := case_when(
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF",
    Method == "CNN" ~ "CNN",
    Method == "CF_base" ~ "CF-base"
  )] %>%
  .[, Method := factor(Method, levels = c("RF", "BRF", "CNN", "CF-base"))] %>%
  ggplot() +
  geom_point(aes(x = true_te_base, y = te_base), size = 0.5) +
  geom_abline(aes(intercept = 0, slope = 1), color = "red", show.legend = TRUE) +
  facet_grid(Treatment ~ Method) +
  guides(
    fill = guide_legend(keywidth = 1, keyheight = 1),
    linetype = guide_legend(keywidth = 3, keyheight = 1),
    colour = guide_legend(keywidth = 3, keyheight = 1)
  ) +
  labs(y = "Estimated Treatment Effect (kg/ha)") +
  labs(x = "True Treatment Effect (kg/ha)") +
  theme_few() +
  theme(
    strip.text.x = element_text(size = 12, face = "bold"),
    strip.text.y = element_text(size = 12, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  theme_figure
```
